\pkg{regsem}: Regularized Structural Equation Modeling

### 2017-03-07 draft1.Rmd
add

In using lasso penalties, difficulties emerge when the scale of variables differ dramatically. By only using one value of $\lambda$, this can add appreciable bias to the resulting estimates [e.g. @fan2001variable]. One method proposed for overcoming this limitation is the adaptive lasso [@zou2006adaptive]. Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (maximum likelihood estimate in SEM). This manifests itself as:
$$
F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
$$
\noindent
with, following the same form for the lasso, the soft-thresholding update is:
[\\]: ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf
$$
S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
$$
\noindent
In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant, parameters. Note that one limitation of this approach for SEM models is that the model needs to be estimable with maximum likelihood. Particularly for models with large numbers of variables, in relation to sample size, this may not be possible.

@@

@@

```{r,eval=FALSE}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
```

@@

@@

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrrrr}
		\hline
		& ML & lasso & alasso & SCAD & MCP \\ 
		\hline
		c1 -$>$ i & 0.17 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c2 -$>$ i & -0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c3 -$>$ i & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c4 -$>$ i & 0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c5 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c6 -$>$ i & -0.52* & 0.00 & 0.00 & 0.00 & -0.24 \\ 
		c7 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c8 -$>$ i & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c9 -$>$ i & 0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c10 -$>$ i & -0.12 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c1 -$>$ s & 1.47* & 1.44 & 1.60 & 1.62 & 1.61 \\ 
		c2 -$>$ s & 0.32* & 0.20 & 0.29 & 0.35 & 0.34 \\ 
		c3 -$>$ s & 0.21 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
		c4 -$>$ s & -0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c5 -$>$ s & -0.25 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c6 -$>$ s & 0.37* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c7 -$>$ s & -0.21 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c8 -$>$ s & 0.27* & 0.04 & 0.00 & 0.00 & 0.00 \\ 
		c9 -$>$ s & -0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		c10 -$>$ s & 0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
		BIC & 3530.61 & 3484.27 & 3475.40 & 3474.85 & 3476.96 \\ 
		\hline
	\end{tabular}
\caption{Parameter estimates for the final models across five estimation methods. Note that * represent significant parameters at p < .05 for maximum likelihood estimation.}
\end{table}

While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect. The lasso and MCP mistakenly identified one false effect each. As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.

To compare the performance of each penalization method further, particularly in the presence of small number of parameters to sample size ratios, a small scale simulation study was conducted. The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size. Each run was replicated 200 times, with the corresponding code in the Appendix. The results are displayed in Table *

@@

@@

## Limitation

>>>>

In using lasso penalties, difficulties emerge when the scale of variables differ dramatically. By only using one value of $\lambda$, this can add appreciable bias to the resulting estimates [e.g. @fan2001variable]. One method proposed for overcoming this limitation is the adaptive lasso [@zou2006adaptive]. Instead of penalizing parameters directly, each parameter is scaled by the un-penalized estimated (maximum likelihood estimate in SEM). This manifests itself as:
$$
F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
$$
\noindent
with, following the same form for the lasso, the soft-thresholding update is:

[\\]: ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf

$$
S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
$$
\noindent
In this, larger penalties are given for non-significant (smaller) parameters, limiting the bias in estimating larger, significant, parameters. Note that one limitation of this approach for SEM models is that the model needs to be estimable with maximum likelihood. Particularly for models with large numbers of variables, in relation to sample size, this may not be possible.

@@

After a final model (penalty) is chosen, user's have the option either just use the output from \code{cv_regsem()}, or the final model can be re-run with either \code{regsem()} or \code{multi_optim()} to attain additional information. In the model above, the best fitting penalty, according to the BIC, is $\lambda=0$. However, for demonstration purposes, we can choose a penalty of 0.2. With this, the model is re-run with \code{regsem()}

```{r, message=FALSE, warning=FALSE}
mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
#summary(mod.out)
```

Note that the arguments used above correspond to the same arguments in \code{multi_optim()}. However, \code{multi_optim()} has additional optional arguments corresponding to the number or random starts to try. Additional fit indices can be attained through the \code{fit_indices()} function.

```{r}
fit_indices(mod.out)
```
\noindent
These same fit measures can be accessed through \code{cv_regsem}, through changing the defaults with the \code{fit.ret=c("rmsea","BIC")} argument. Finally, instead of assessing these fit indices on the same sample that the models were run on, a holdout dataset could be used. This can be done two ways: either with \code{cv_regsem(...,fit.ret2="test")} or with \code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the holdout covariance matrix.

@@

```{r,eval=FALSE}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
```

@@

mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & ML & lasso & alasso & SCAD & MCP \\ 
  \hline
c1 -$>$ i & 0.92* & 0.72 & 0.91 & 0.94 & 0.92 \\ 
  c2 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c3 -$>$ i & 0.10 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c4 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c5 -$>$ i & 0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c6 -$>$ i & -0.25 & 0.00 & 0.00 & 0.00 & -0.19 \\ 
  c7 -$>$ i & 0.11 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c8 -$>$ i & -0.13 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c9 -$>$ i & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c10 -$>$ i & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c1 -$>$ s & 1.18* & 1.09 & 1.22 & 1.24 & 1.24 \\ 
  c2 -$>$ s & 0.29* & 0.19 & 0.28 & 0.35 & 0.35 \\ 
  c3 -$>$ s & 0.18 & 0.09 & 0.00 & 0.00 & 0.00 \\ 
  c4 -$>$ s & -0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c5 -$>$ s & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c6 -$>$ s & 0.25* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c7 -$>$ s & -0.18 & -0.04 & 0.00 & 0.00 & 0.00 \\ 
  c8 -$>$ s & 0.26* & 0.10 & 0.00 & 0.00 & 0.00 \\ 
  c9 -$>$ s & -0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c10 -$>$ s & 0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  BIC & 3465.28 & 3427.46 & 3415.05 & 3414.38 & 3417.20 \\ 
   \hline
\end{tabular}
\caption{Parameter estimates for the final models across five estimation methods. Note that * represent significant parameters at p < .05 for maximum likelihood estimation.}
\end{table}

While every regularization method erroneously set both simulated true intercept effects as zero (as in maximum likelihood, which accounts for these errors), both the adaptive lasso and SCAD correctly identified every true zero effect. The lasso identified two false effects while the MCP mistakenly identified one. Additionally, the lasso estimation of the true effects was attentuated in comparison to the other regularization methods. This is in line with previous research (cite), necessitating the use of a two-step relaxed lasso method [@meinshausen2007relaxed, see @jacobucci2016regularized] As expected given the small ratio between number of estimated parameters and sample size, maximum likelihood mistakenly identified 3 false effects as significant.

To compare the performance of each penalization method further, particularly in the presence of small number of parameters to sample size ratios, a small scale simulation study was conducted. The same model and effects was kept, but the sample size was varied to include 80, 200, and 1000 to demonstrate how maximum likelihood estimation of effects improves as sample size increases, while each of the regularization methods performs well regardless of sample size. Each run was replicated 200 times. The results are displayed in Table *

@@

This paper provides an introduction to the \pkg{regsem} package, outlining the mathematical details of the regularized SEM method and the usage of the package itself.

@@

## Limitations

With highly constrained structural equation models, achieving convergence can be particularly problematic in using \pkg{regsem}. For instance, with the latent change score model (cite jack), Bayesian regularization methods have less difficulty in reaching convergence across chains (cite chapter). With the advent of additional sparsity inducing priors, along with new forms of software such as STAN (cite stan), for some models it may be more appropriate to use these Bayesian regularization methods over their frequentist counterparts.

### 2017-03-07 draft1.tex
add

In using lasso penalties, difficulties emerge when the scale of
variables differ dramatically. By only using one value of \(\lambda\),
this can add appreciable bias to the resulting estimates (e.g. Fan and
Li 2001). One method proposed for overcoming this limitation is the
adaptive lasso (Zou 2006). Instead of penalizing parameters directly,
each parameter is scaled by the un-penalized estimated (maximum
likelihood estimate in SEM). This manifests itself as: \[
F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
\] \noindent
with, following the same form for the lasso, the soft-thresholding
update is:
\href{High\%20dimensional\%20statistics\%20p.\%2032}{\textbackslash{}}:
\url{ftp://ftp.stat.math.ethz.ch/Teaching/buhlmann/advanced-comput-statist/notes1.pdf}
\[
S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
\] \noindent
In this, larger penalties are given for non-significant (smaller)
parameters, limiting the bias in estimating larger, significant,
parameters. Note that one limitation of this approach for SEM models is
that the model needs to be estimable with maximum likelihood.
Particularly for models with large numbers of variables, in relation to
sample size, this may not be possible.

@@

@@

\begin{CodeChunk}
\begin{CodeInput}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8+ c9+ c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrrr}
        \hline
        & ML & lasso & alasso & SCAD & MCP \\ 
        \hline
        c1 -$>$ i & 0.17 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c2 -$>$ i & -0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c3 -$>$ i & 0.01 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c4 -$>$ i & 0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c5 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c6 -$>$ i & -0.52* & 0.00 & 0.00 & 0.00 & -0.24 \\ 
        c7 -$>$ i & 0.20 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c8 -$>$ i & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c9 -$>$ i & 0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c10 -$>$ i & -0.12 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c1 -$>$ s & 1.47* & 1.44 & 1.60 & 1.62 & 1.61 \\ 
        c2 -$>$ s & 0.32* & 0.20 & 0.29 & 0.35 & 0.34 \\ 
        c3 -$>$ s & 0.21 & 0.10 & 0.00 & 0.00 & 0.00 \\ 
        c4 -$>$ s & -0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c5 -$>$ s & -0.25 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c6 -$>$ s & 0.37* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c7 -$>$ s & -0.21 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c8 -$>$ s & 0.27* & 0.04 & 0.00 & 0.00 & 0.00 \\ 
        c9 -$>$ s & -0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        c10 -$>$ s & 0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
        BIC & 3530.61 & 3484.27 & 3475.40 & 3474.85 & 3476.96 \\ 
        \hline
    \end{tabular}
\caption{Parameter estimates for the final models across five estimation methods. Note that * represent significant parameters at p < .05 for maximum likelihood estimation.}
\end{table}

While every regularization method erroneously set both simulated true
intercept effects as zero (as in maximum likelihood, which accounts for
these errors), both the adaptive lasso and SCAD correctly identified
every true zero effect. The lasso and MCP mistakenly identified one
false effect each. As expected given the small ratio between number of
estimated parameters and sample size, maximum likelihood mistakenly
identified 3 false effects as significant.

To compare the performance of each penalization method further,
particularly in the presence of small number of parameters to sample
size ratios, a small scale simulation study was conducted. The same
model and effects was kept, but the sample size was varied to include
80, 200, and 1000 to demonstrate how maximum likelihood estimation of
effects improves as sample size increases, while each of the
regularization methods performs well regardless of sample size. Each run
was replicated 200 times, with the corresponding code in the Appendix.
The results are displayed in Table *

@@

\subsection{Limitation}\label{limitation}

@@

>>>>

In using lasso penalties, difficulties emerge when the scale of
variables differ dramatically. By only using one value of \(\lambda\),
this can add appreciable bias to the resulting estimates (e.g. Fan and
Li 2001). One method proposed for overcoming this limitation is the
adaptive lasso (Zou 2006). Instead of penalizing parameters directly,
each parameter is scaled by the un-penalized estimated (maximum
likelihood estimate in SEM). This manifests itself as: \[
F_{alasso} = F_{ML} + \lambda \| \theta_{ML}^{-1} * \theta_{pen} \|_{1}
\] \noindent
with, following the same form for the lasso, the soft-thresholding
update is:

\[
S(\theta_{j})= sign(\theta_{j})(|\theta_{j}|-\frac{\lambda}{2|\theta_{j}|})_{+}
\] \noindent
In this, larger penalties are given for non-significant (smaller)
parameters, limiting the bias in estimating larger, significant,
parameters. Note that one limitation of this approach for SEM models is
that the model needs to be estimable with maximum likelihood.
Particularly for models with large numbers of variables, in relation to
sample size, this may not be possible.

@@

After a final model (penalty) is chosen, user's have the option either
just use the output from \code{cv_regsem()}, or the final model can be
re-run with either \code{regsem()} or \code{multi_optim()} to attain
additional information. In the model above, the best fitting penalty,
according to the BIC, is \(\lambda=0\). However, for demonstration
purposes, we can choose a penalty of 0.2. With this, the model is re-run
with \code{regsem()}

\begin{CodeChunk}
\begin{CodeInput}
mod.out <- regsem(out, type="lasso", pars_pen=c(1:9),lambda=0.2)
#summary(mod.out)
\end{CodeInput}
\end{CodeChunk}

Note that the arguments used above correspond to the same arguments in
\code{multi_optim()}. However, \code{multi_optim()} has additional
optional arguments corresponding to the number or random starts to try.
Additional fit indices can be attained through the \code{fit_indices()}
function.

\begin{CodeChunk}
\begin{CodeInput}
fit_indices(mod.out)
\end{CodeInput}
\begin{CodeOutput}
$Data_Type
[1] "Train"

$fits
          Fmin         varFit              p          chisq        p.chisq 
       0.69087        0.00000        9.00000      415.90286        0.00000 
          nfac             df           npar              N baseline.chisq 
       1.00000       31.00000       14.00000      301.00000      918.85159 
   baseline.df           logl            ncp          rmsea    rmsea.lower 
      36.00000    -3903.04360        1.28301        0.20344        0.18598 
   rmsea.upper     rmsea.pval            CFI            TLI            BIC 
            NA        0.00000        0.56402        0.49370     7885.98674 
           AIC           CAIC         EBIC.5        EBIC.25 
    7834.08719     7983.11043     8051.12157     8017.06459 
\end{CodeOutput}
\end{CodeChunk}

\noindent
These same fit measures can be accessed through \code{cv_regsem},
through changing the defaults with the \code{fit.ret=c("rmsea","BIC")}
argument. Finally, instead of assessing these fit indices on the same
sample that the models were run on, a holdout dataset could be used.
This can be done two ways: either with
\code{cv_regsem(...,fit.ret2="test")} or with
\code{fit_indices(model,CV=TRUE,CovMat=)} and specifying the name of the
holdout covariance matrix.

@@

\begin{CodeChunk}
\begin{CodeInput}
mod1 <- "
i =~ 1*x1 + 1*x2 + 1*x3 + 1*x4
s =~ 0*x1 + 1*x2 + 2*x3 + 3*x4
i ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
s ~ c1 + c2 + c3 + c4 + c5 + c6 + c7 + c8 + c9 + c10
"
lav.growth <- growth(mod1,dat,fixed.x=T)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & ML & lasso & alasso & SCAD & MCP \\ 
  \hline
c1 -$>$ i & 0.92* & 0.72 & 0.91 & 0.94 & 0.92 \\ 
  c2 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c3 -$>$ i & 0.10 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c4 -$>$ i & 0.07 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c5 -$>$ i & 0.04 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c6 -$>$ i & -0.25 & 0.00 & 0.00 & 0.00 & -0.19 \\ 
  c7 -$>$ i & 0.11 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c8 -$>$ i & -0.13 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c9 -$>$ i & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c10 -$>$ i & 0.09 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c1 -$>$ s & 1.18* & 1.09 & 1.22 & 1.24 & 1.24 \\ 
  c2 -$>$ s & 0.29* & 0.19 & 0.28 & 0.35 & 0.35 \\ 
  c3 -$>$ s & 0.18 & 0.09 & 0.00 & 0.00 & 0.00 \\ 
  c4 -$>$ s & -0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c5 -$>$ s & -0.18 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c6 -$>$ s & 0.25* & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c7 -$>$ s & -0.18 & -0.04 & 0.00 & 0.00 & 0.00 \\ 
  c8 -$>$ s & 0.26* & 0.10 & 0.00 & 0.00 & 0.00 \\ 
  c9 -$>$ s & -0.06 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  c10 -$>$ s & 0.08 & 0.00 & 0.00 & 0.00 & 0.00 \\ 
  BIC & 3465.28 & 3427.46 & 3415.05 & 3414.38 & 3417.20 \\ 
   \hline
\end{tabular}
\caption{Parameter estimates for the final models across five estimation methods. Note that * represent significant parameters at p < .05 for maximum likelihood estimation.}
\end{table}

While every regularization method erroneously set both simulated true
intercept effects as zero (as in maximum likelihood, which accounts for
these errors), both the adaptive lasso and SCAD correctly identified
every true zero effect. The lasso identified two false effects while the
MCP mistakenly identified one. Additionally, the lasso estimation of the
true effects was attentuated in comparison to the other regularization
methods. This is in line with previous research (cite), necessitating
the use of a two-step relaxed lasso method (Meinshausen 2007, see
Jacobucci, Grimm, and McArdle (2016)) As expected given the small ratio
between number of estimated parameters and sample size, maximum
likelihood mistakenly identified 3 false effects as significant.

To compare the performance of each penalization method further,
particularly in the presence of small number of parameters to sample
size ratios, a small scale simulation study was conducted. The same
model and effects was kept, but the sample size was varied to include
80, 200, and 1000 to demonstrate how maximum likelihood estimation of
effects improves as sample size increases, while each of the
regularization methods performs well regardless of sample size. Each run
was replicated 200 times. The results are displayed in Table *

@@

\subsection{Limitations}\label{limitations}

With highly constrained structural equation models, achieving
convergence can be particularly problematic in using \pkg{regsem}. For
instance, with the latent change score model (cite jack), Bayesian
regularization methods have less difficulty in reaching convergence
across chains (cite chapter). With the advent of additional sparsity
inducing priors, along with new forms of software such as STAN (cite
stan), for some models it may be more appropriate to use these Bayesian
regularization methods over their frequentist counterparts.

@@

\hypertarget{ref-meinshausen2007relaxed}{}
Meinshausen, Nicolai. 2007. ``Relaxed Lasso.'' \emph{Computational
Statistics \& Data Analysis} 52 (1). Elsevier: 374--93.
